Optimal (Multiway) Spatial Joins

### 2024-06-01 5.2.tex
5.2

\noindent \underline{\em Proof of Statement (1).} Consider any tuple $\bm{t} = (r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$. Let $h$ be the full segment of $h'$. Following our conventions, $B_\bm{t}$ denotes the intersection point of $h'$ and $v$, and it is covered by the rectangles $r_1,...,r_{k-3}$. As $h$ is the full segment of $h'$, $B_\bm{t} \in h$, and $B_\bm{t}$ is also the intersection of $h$ and $v$. Let $r_{k-2}$ be an arbitrary rectangle in $\contained_{R_{k-2}}(\bm{t})$. By the definition of $\contained_{R_{k-2}}(\bm{t})$, $r_{k-2}$ covers the effective segment of $h'$, whose right enpoint is $B_{\bm{t}}$. Therefore, $B_{\bm{t}}$ is covered by each of the rectangles $r_1,...,r_{k-2}$. Equivalently, $h \cap v \bigcap_{i = 1}^{k-2} r_i = B_\bm{t} \neq \emptyset$. Hence,
$\bm{t} \in \J(R_1,...,R_{k-2},H,V)$. To show that $\bm{t} \in \J_2$, we only need to prove that $r_{k-2}$ covers the left endpoint of $h$. It is true because $r_{k-2}$ covers the effective segment of $h'$, whose left endpoint is the same as the left endpoint of $h$.

@@

\noindent \underline{\em Proof of Statement (2).} Let $(r_1,...,r_{k-2},h,v)$, $h'$, $\bm{t}$ be as defined in the statement. First, we prove that $\bm{t}\in \J(R_1,...,R_{k-3}, H', V)$.
Let $p$ be the intersection of $h$ and $v$. Since $(r_1,...,r_{k-2},h,v)\in \J_2$, $p$ is in $r_i$ for $i \in [k-2]$.
We argue that $p$ is also the intersection of $h'$ and $v$, which implies that $h'\cap v$ is covered by $r_i$, $i \in [k-3]$ and $\bm{t} \in \J(R_1,...,R_{k-3},H',V)$. Since $p \in v$, it suffices to show that $p \in h'$. Let $h = [x_1,x_2]\times y$ and $p = (x,y)$. Since $h' \subseteq h$, we can denote $h'$ as $[x_1, x_2'] \times y$, where $x_1 \le x_2' \le x_2$. Then, we only need to show that $x \in [x_1, x_2']$. Since $p \in h$, $x \ge x_1$. Since $(r_1,...,r_{k-2},h,v) \in \J_2$, $r_{k-2}$ is a left-end covering rectangle of $h$ in $R_{k-2}$, that also covers the point $p \in h$. By the definition of trimmed segment (see Secton~\ref{sec:hv:type2}), the x-coordinate of $p$ should not exceed $x_2'$. Hence, $x \in [x_1, x_2']$, and $p \in h'$.

>>>>

\noindent \underline{\em Proof of Statement (1).} Consider any tuple $\bm{t} = (r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$. Let $h$ be the full segment of $h'$. Following our conventions, $B_\bm{t}$ denotes the intersection point of $h'$ and $v$, and it is covered by the rectangles $r_1,...,r_{k-3}$. As $h$ is the full segment of $h'$, we have $B_\bm{t} \in h$, and $B_\bm{t}$ is also the intersection of $h$ and $v$. Let $r_{k-2}$ be an arbitrary rectangle in $\contained_{R_{k-2}}(\bm{t})$. By the definition of $\contained_{R_{k-2}}(\bm{t})$, $r_{k-2}$ covers the effective segment of $h'$, whose right enpoint is $B_{\bm{t}}$. Therefore, $B_{\bm{t}}$ is covered by each of the rectangles $r_1,...,r_{k-2}$. Equivalently, $h \cap v \bigcap_{i = 1}^{k-2} r_i = B_\bm{t} \neq \emptyset$. Hence,
$\bm{t} \in \J(R_1,...,R_{k-2},H,V)$. To show that $\bm{t} \in \J_2$, we only need to prove that $r_{k-2}$ covers the left endpoint of $h$. It is true because $r_{k-2}$ covers the effective segment of $h'$, whose left endpoint is the same as the left endpoint of $h$.

@@

\noindent \underline{\em Proof of Statement (2).} Let $(r_1,...,r_{k-2},h,v)$, $h'$, $\bm{t}$ be as defined in the statement. First, we prove that $\bm{t}\in \J(R_1,...,R_{k-3}, H', V)$. It suffices to show that the intersection of $h'$ and $v$ is contained in $r_1,...,r_{k-3}$. We will prove this by showing that $h'\cap v$ is the same as $h\cap v$, which is covered by $r_1,...,r_{k-2}$, because $\bm{t} \in \J(R_1,...,R_{k-2},H,V)$.

Let $p$ be the intersection of $h$ and $v$. Since $h' \subseteq h$, the intersection of $h'$ and $v$ is either empty or the same as $p$.
Therefore, to prove that $h' \cap v = p$, we only need to show that $p \in h'$. Let $h = [x_1,x_2]\times y$ and $p = (x,y)$. Since $h' \subseteq h$, we can denote $h'$ as $[x_1, x_2'] \times y$, where $x_1 \le x_2' \le x_2$. Then, $p \in h'$ is equivalent to $x \in [x_1, x_2']$. Since $p \in h$, we have $x \ge x_1$. By the definition of trimmed segmemt, $(x_2',y)$ is the rightmost point on $h$ satisfying that a left-end covering rectangle of $h$ in $R_{k-2}$ covers it. As $(r_1,...,r_{k-2},h,v) \in \J_2$, the point $p \in h$ is covered by the rectangle $r_{k-2}$, which is a left-end covering rectangle of $h$. Therefore, the x-coordinate of $p$ should not exceed $x_2'$. As a result, we have $x \in [x_1, x_2']$, and $p \in h'$.
